Response to reviewers article 4780

### 2023-06-18 review/B-response.Rmd
response to reviewers done

The cubble class has been refactored as suggested by reviewer 1. Now the cubble class has two sub-classes:

@@

The package documentation have been substantially improved, specifically, [...]. A new version of the package (v0.3.0) is now available on CRAN.

@@

**\textcolor{purple}{The suggested class implemented has been adopted, see The Package section in the Summary of Main Changes. The codes on checking key values from multiple tables have been moved to a separate function check\_key() and reflected in the example 5.1 now. The function as\_cubble() now returns nested cubbles.}**

@@

The user would need to visit the documentation of tsibble in order to understand the meaning of the key and index. But the relationship to tsibble is not even mentioned in the docs.
The documentation of the key and index is not perfect in tsible either, but sheds some more light on their role:

@@

The doc states:

@@

**\textcolor{purple}{Documentation of the package has been substantially improved with a focus on clarifying the input arguemnt types. For the specific example of as\_cubble(), the mentioned arguments now state:  }**

@@

**\textcolor{purple}{TODO: more here}**

@@

**\textcolor{purple}{the spatial attribute can be checked with function spaital(<cubbble\_obj>)}**

@@

**\textcolor{purple}{TODO}**

@@

  - on p6, section 3.2, yet another reason to call this data structure "cubble_temporal" instead of the semantically unobvious "long". **\textcolor{purple}{see paragraph 4 under section The paper in this response.}**

>>>>

The cubble class has been re-factored as suggested by reviewer 1. Now the cubble class has two sub-classes:

@@

Other noticeable changes made to the package include:

  - The syntax for creating a cubble from separate spatial and temporal component has been changed from `as_cubble(list(spatial = ..., temporal = ...), ...)` to `make_cubble(spatial = ..., temporal = ..., ...)`. 
  - The new added toy data for demonstration: `stations` and `stations_sf` (the spatial component of three airport weather stations and it as an sf object), `meteo` and `meteo_ts` (the temporal component of the three weather stations and it as a tsibble object).
  - A new version of the package (v0.3.0) is now available on CRAN.

@@

**\textcolor{purple}{The suggested class implemented has been adopted, see The Package section in the Summary of Main Changes in this reponse. The codes on checking key values from multiple tables have been moved to a separate function check\_key() and reflected in the example 5.1 now. The function as\_cubble() now returns nested cubbles.}**

@@

The user would need to visit the documentation of tsibble in order to understand the meaning of the key and index. But the relationship to tsibble is not even mentioned in the docs.
The documentation of the key and index is not perfect in tsibble either, but sheds some more light on their role:

@@

````
The doc states:

@@

**\textcolor{purple}{Documentation of the package has been substantially improved with a focus on clarifying the input arguemnt types. For the specific example of as\_cubble(), the documentation now states:}**

@@

**\textcolor{purple}{cubble() is the class constructor and the documentation now states "Create a cubble object". as\_cubble() is the coercion function and documented as "Coerce foreign objects into a cubble object".}**

@@

**\textcolor{purple}{The spatial attribute can be checked with function spaital(<cubbble\_obj>).}**

@@

**\textcolor{purple}{Cubble internally uses tidyr::nest() in the construction of a nested/spatial cubble (hence the name). We now mention the tidyr::nest() under the cubble attributes in Section 2.1 as an implication of rows being uniquely identified in the nested cubble.}**

@@

  - on p6, section 3.2, yet another reason to call this data structure "cubble_temporal" instead of the semantically obvious "long". **\textcolor{purple}{see paragraph 4 under section The paper in this response.}**
